CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review to improve reproducibility

### 2021-02-24 codecheck-paper.tex
final fixes

ACM: Association for Computing Machinery; 
ECRs: Early Career Researchers;
RCR: Replicated Computational Results;
TOMS: Transactions on Mathematical Software;
\clearpage

>>>>

ACM: Association for Computing Machinery; 
ECRs: Early Career Researchers;
RCR: Replicated Computational Results;
TOMS: Transactions on Mathematical Software.
\clearpage
